---
title: "How does body mass differ from penguin species?"
author: "Du Du"
date: "2026-09-22"
format: html
engine: knitr
---

This post studies how penguins' species have impact on their corresponding body mass.

License: The data source "penguins" comes from:
[Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/), collected by Dr. Kristen Gorman and Palmer Station Antarctica LTER. The data are available under the CC0 license.

## Loading library and inspecting data
```{r}
#| label: setup&inspect-data
#| message: false
#| warning: false

library(tidyverse)
library(palmerpenguins)
dim(penguins)
colSums(is.na(penguins))
```

## Cleaning data
```{r}
#| label: cleaning-data (dropping NAs only in column body_mass_g)

penguins_clean <-
    penguins |>
    drop_na(body_mass_g)
```

## Analyzing body mass by species
```{r}
#| label: Analyzing-body_mass-by-species

penguins_summary <-
    penguins_clean |>
    group_by(species) |>
    summarise(
        n = n(),
        mean_mass_g = mean(body_mass_g),
        median_mass_g = median(body_mass_g),
        sd_mass_g = sd(body_mass_g),
        .groups = "drop"
    )

knitr::kable(
    penguins_summary,
    digits = 1,
    caption = "Body mass summary by penguin species(grams)."
)
```

## Visualizing the summary using a boxplot
```{r}
#| label: Visualizing-species-with-their-body-mass-figures
#| fig-cap: "Body mass of penguins by species"

ggplot(penguins_clean, aes(x = species, y = body_mass_g, fill = species)) + geom_boxplot()+ 
    labs(
        x = 'Penguin Species',
        y = 'Body Mass (g)'
    ) +
    theme_minimal() +
    theme(legend.position = "none")

```

## Findings
After removing the two rows with nas, the outcome shows that 'Gentoo' species typically has the highest body mass across the three penguin species.